Verifying Spatial Properties of Array Computations

### 2017-04-15 oopsla17/study.tex
switch to si unit format in table

\item Most loop-array computations of the previous form read
from a arrays with a \emph{contiguous} pattern, \eg{}:
%
\begin{minted}{fortran}
do i = 1, n
  b(n) = (a(i) + a(i+1)) / 2.0
\end{minted}
%
\item Most loop-array computations of the previous form read
from arrays with a pattern that includes the immediate
neighbours (offsets of 1 from the induction variables);

@@

%\begin{enumerate}
%\item Loops over arrays mainly read from arrays with a static pattern
%based on constant offsets from (base or dervied) induction variables;
%\end{enumerate}

%\begin{tabular}
%Neighbourhood or Constant Affine RHS &  Total
%\end{tabular}

\noindent
We identified $108,773$ instances of assignments within loops in
which an array subscript flows to the right-hand side. We refer
to each one of these as an \emph{array computation}.
We performed the classification described in the methodology,
and then grouped the data by based only on the right-hand side
classification:
%%
\begin{center}
\begin{tabular}{lrrcc}
\textbf{RHS classification} & \textbf{Number} & \textbf{\%} &
\textit{grouping 1} & \textit{grouping 2} \\ \hline
Affine                          & 34        & 0.03\%  &
                                                            \multirow{4}{*}{92.61\%}
  \\ \cline{1-3}\cline{5-5}
All constant                    & 12160     & 11.18\%  \\ \cline{1-3}\cline{5-5}
Neighbourhood                   & 65334     & 60.06\% &
                                                          & \multirow{2}{*}{81.4\%}
                                                           \\ \cline{1-3}
Neighbourhood + constants       & 23209     & 21.34\%  \\ \hline
Other                           & 8036      & 7.39\%  \\ \hline \hline
Total                           & 108773    &  \\
\end{tabular}
\end{center}

\noindent
Since, affine, consant, and neighbour are all static patterns, we
group them (\textit{grouping 1}) to see that $92.61\%$ of the array computations have
a static pattern that are either constants or constant of offsets
of base/derived induction variables, thus confirming
\emph{hypothesis 1}. Note that affine (derived induction variables) are very
rare. Overwhelmingly the main category is neighbourhood offsets
(\emph{grouping 2})
(possibly mixed with constants in some dimensions), at $81.4\%$ in
total. The ``affine + constants'' class is not represented at all.

>>>>

\item Most loop-array computations of the previous form read
from arrays with a \emph{contiguous} pattern, \eg{}:
%
\begin{minted}{fortran}
do i = 1, n
  b(n) = (a(i) + a(i+1)) / 2.0
\end{minted}
%
\item Most loop-array computations of the previous form read
from arrays with a pattern that includes the immediate
neighbours (offsets of 1 from the induction variables);

@@

We first consider the initial hypotheses in turn again the collected data.
%
\begin{enumerate}
\item Loops over arrays mainly read from arrays with a static pattern
based on constant offsets from (base or dervied) induction variables;
\end{enumerate}
%
We identified $108,773$ instances of assignments within loops in
which an array subscript flows to the right-hand side. We refer
to each one of these as an \emph{array computation}.
We performed the classification described above
and grouped the data by the right-hand side classification only:
%%
\begin{center}
\begin{tabular}{lS[table-format=4]S[table-format=2.2]cc}
\textbf{RHS classification} & \textbf{Number} & \% &
\textit{grouping 1} & \textit{grouping 2} \\ \hline
Affine                          & 34        & 0.03\%  &
                                                            \multirow{4}{*}{92.61\%}
  \\ \cline{1-3}\cline{5-5}
All constant                    & 12160     & 11.18\%  \\ \cline{1-3}\cline{5-5}
Neighbourhood                   & 65334     & 60.06\% &
                                                          & \multirow{2}{*}{81.4\%}
                                                           \\ \cline{1-3}
Neighbourhood + constants       & 23209     & 21.34\%  \\ \hline
Other                           & 8036      & 7.39\%  \\ \hline \hline
Total                           & 108773    &  \\
\end{tabular}
\end{center}
%
\noindent
Since, affine, consant, and neighbour are all static patterns, we
group them (\textit{grouping 1}) to see that $92.61\%$ of the array
computations (\numexpr(100,737))
 have a static pattern that are either constants or
constant offsets of base/derived induction variables, confirming
\emph{hypothesis 1}. Note that affine (derived induction variables)
are rare. Overwhelmingly, the main category is neighbourhood
offsets (\emph{grouping 2}) (possibly mixed with constants in some
dimensions), at $81.4\%$ in total. The ``affine + constants'' class is
not represented at all.
%
\begin{enumerate}[resume]
\item Most loop-array computations of the previous form read
from arrays with a \emph{contiguous} pattern, \eg{}:
%
\begin{minted}{fortran}
do i = 1, n
  b(n) = (a(i) + a(i+1)) / 2.0
\end{minted}
%
\item Most loop-array computations of the previous form read
from arrays with a pattern that includes the immediate
neighbours (offsets of 1 from the induction variables);
\end{enumerate}
%
Focussing on grouping1 
\end{enumerate}
